---
title: "index"
output: 
  flexdashboard::flex_dashboard:
    orientation: row
    vertical_layout: fill
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(here)
library(ggraph)
library(igraph)
library(plotly)
library(shiny)
library(dplyr)
library(here)
library(ggplot2)
library(ggraph)
library(tidygraph)
library(writexl)
library(RColorBrewer)
library(gt)
```

```{r data}
##Commented this code out for later application...to use in more real time application for summer encompass workshop
#read_csv("DATA/ORCIDS W1 SP21 RAW.csv") -> DBdata
#select(DBdata, 3,8:13) -> DBdata_1 #MessageID, Forum Name, Parent Post/InReplyTo, ThreadID, AuthorFrom
#select(DBdata_1, 1,5) -> messageID #MessageID, AuthorFrom
#na.omit(DBdata_1) -> DBdata_2 #Removes initial
#select(DBdata_2, 2:5) -> DBdata_3 #Forum Name, Parent Post/InReplyTo, ThreadID, AuthorFrom
 # colnames(DBdata_3)[2] <- c("MessageID") #change InReplyTo to message ID
  #colnames(DBdata_3)[4] <- c("AuthorFrom") 
#inner_join(messageID, DBdata_3, by = "MessageID") -> DBdata_4
#colnames(DBdata_4)[2] <- c("AuthorTo")
#DBdata_4[c(3,5,2,1,4)] -> DBdata_5
#DBdata_5[order(DBdata_5$"ForumName"),] -> DBdata_6
#select(DBdata_6, 2,3) -> DBdata_6
#gr1 <- igraph::graph_from_data_frame(DBdata_6, directed = TRUE)
```

```{r}
#library(brainGraph)
#Cohesiveness <- function(gr){ 
 # Den = edge_density(gr)
  #Recip = reciprocity(gr)
  #Eff = brainGraph::efficiency(gr, type = "global")
  #Diam = diameter(gr)
  #Trans = transitivity(gr)
  #Cent = centralization.degree(gr, mode = "all")$centralization
  #df = tibble(Den, Recip, Eff, Diam, Trans, Cent)
  #return(df)  
#}
#the following code organizes cohesiveness results into a data frame
#as.tibble(Cohesiveness(gr1)) -> newdf
```

# Network Plots

### Discussion Forum Interactions

```{r}
#generating the 1-mode network for comparison with the 2-mode
read_csv("DATA/SP2021_C1_WKSP1_Mod_1_4_coded.csv") -> edges.1mode
read_csv("DATA/SP2021_C1_workshop_1_nodes_w_topics.csv") -> nodes
slice(nodes, 1:17) -> nodes.1mode
net.1mode <- graph_from_data_frame(d = edges.1mode, vertices = nodes.1mode, directed = TRUE)
couls <- brewer.pal(3, "Set1")
my_colors <- couls[as.numeric(as.factor(V(net.1mode)$position))]
E(net.1mode)$weight <- 1 #assign weight of one to each edge
net.1mode.1 <-simplify(net.1mode, edge.attr.comb=list(weight="sum")) #collapse multiple edges into weighted according to sum
plot(net.1mode.1, layout = layout_with_fr, vertex.color=my_colors, vertex.label.color="black", vertex.label.dist=1, edge.arrow.size=.01, vertex.size=8, vertex.label=NA, edge.width=E(net.1mode.1)$weight)
# Add a legend
legend("bottomleft", legend=levels(as.factor(V(net.1mode)$position)), col = couls , bty = "n", pch=20 , pt.cex = 1, cex = .5, text.col=couls, horiz = FALSE, inset = c(.01, .01))
```


### Participant Topic Interactions

```{r}
read_csv("DATA/SP2021_C1_workshop_1_edges_w_topics.csv") -> edges
select(edges, 1,4) -> edges
read_csv("DATA/SP2021_C1_workshop_1_nodes_w_topics.csv") -> nodes
net <- graph_from_data_frame(d = edges, vertices = nodes, directed = FALSE)
#bipartite_mapping(net) # test to see if bipartite
V(net)$type <- bipartite_mapping(net)$type #distinguishes the nodes by mode
V(net)$color <- ifelse(V(net)$type, "lightblue", "salmon")
V(net)$shape <- ifelse(V(net)$type, "circle", "square")
E(net)$color <- "lightgray"
plot(net, vertex.label.cex = 0.5, vertex.label.color = "black")

```

# More Network Plots

### Participant Discussion Theme Interactions

```{r}


coul <- brewer.pal(5, "Set1")
my_color <- coul[as.numeric(as.factor(V(net)$topic_name))]
plot(net, layout = layout_nicely, vertex.shape=V(net)$position_lab, vertex.color=my_color, vertex.size= 8, vertex.label=NA) 
#shapes are in the csv
# Add a legend
legend("bottomleft", legend=levels(as.factor(V(net)$topic_name))  , col = coul , bty = "n", pch=20 , pt.cex = 1, cex = .5, text.col=coul , horiz = FALSE, inset = c(.01, .01))

```

### Participant Topic Association *1 mode Projection*

```{r}
V(net)$type <- bipartite_mapping(net)$type #distinguishes the nodes by mode
Part_association <- as_incidence_matrix(net) %*% t(as_incidence_matrix(net)) 
diag(Part_association) <- 0
net2 <-graph_from_adjacency_matrix(Part_association) 
EL <- get.edgelist(net2)
EL1 <- as_tibble(EL)
nodes.bp <- slice(nodes, 1:17)
net3 <- graph_from_data_frame(d = EL, vertices = nodes.bp, directed = FALSE)
couls <- brewer.pal(3, "Set1")
E(net3)$weight <- 1 #assign weight of one to each edge
net4<-simplify(net3, edge.attr.comb=list(weight="sum")) #collapse multiple edges into weighted according to sum
my_color <- couls[as.numeric(as.factor(V(net3)$position))]
plot(net4, layout = layout_nicely, vertex.color=my_color, vertex.label.color="black", vertex.label.dist=1, edge.arrow.size=.01, vertex.size=8, vertex.label=NA, edge.width=.5*E(net4)$weight)
legend("bottomleft", legend=levels(as.factor(V(net)$position))  , col = coul , bty = "n", pch=20 , pt.cex = 1, cex = .5, text.col=coul , horiz = FALSE, inset = c(.1, .01))
```

# Centrality

### Individual Centrality

```{r}
Degree <- degree(net3)
Degree <- as_tibble(Degree)
Betweenness = betweenness(net3, normalized = TRUE)
Betweenness <- as_tibble(Betweenness)
Closeness = closeness(net3)
Closeness <- as_tibble(Closeness)
ec <- eigen_centrality(net3, directed=F, weights=E(net3)$weights)$vector
Eg.centr <- as_tibble(ec)
Coreness = graph.coreness(net3)
Coreness <- as_tibble(Coreness)
slice(nodes, 1:17) -> Names
select(Names, Media, position) -> Names
cbind(Names, Degree, Betweenness, Closeness, Eg.centr, Coreness) -> Individual_Centrality
colnames(Individual_Centrality) <- c("Names", "Position","Degree", "Betweenness", "Closeness", "Eigenvector", "Coreness")
gt(Individual_Centrality)
```

# Compare Topic Participant and Participant Participant Networks

### Degree versus Position (Scatterplot)

```{r}
ggplot(data=Individual_Centrality, mapping = aes(x = Position, y = Degree)) + 
  geom_jitter(width = 0, height = .6) +
  geom_smooth() +
  theme_bw()
```


### Degree versus Position (Boxplot)

```{r}
ggplot(data=Individual_Centrality, mapping = aes(x = Position, y = Degree)) + 
  geom_boxplot() +
  theme_bw()
```
















